---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

```{r}
setwd("C:/Krishna/MyProject/DataScience/5_Reproducible_Research")
```

## Loading and preprocessing the data

#####1. Load the data (i.e. read.csv())

```{r}
activity <- read.csv("activity.csv", stringsAsFactors=FALSE)
```

#####2.Process/transform the data (if necessary) into a format suitable for your analysis


```{r}
activity$date <- as.POSIXct(activity$date, format="%Y-%m-%d")
```

## What is mean total number of steps taken per day?

#####1. Calculate the total number of steps taken per day

```{r}
total_activity <- aggregate(activity$steps, by=list(activity$date), FUN=sum, na.rm=TRUE)
names(total_activity) <- c("date", "total")
head(total_activity,10)
```

#####2 Make a histogram of the total number of steps taken each day
```{r}
hist(total_activity$total, 
     col="blue", 
     xlab="Total number of steps", 
     main="Histogram of the total number of steps taken each day")
```

#####3. Calculate and report the mean and median of the total number of steps taken per day
```{r}
mean(total_activity$total)
median(total_activity$total)
```



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
